Interactive Curvature Tensor Visualization on Digital Surfaces\thanks{This work has been mainly funded by \textsc{DigitalSnow} ANR-11-BS02-009, \textsc{KIDICO} ANR-2010-BLAN-0205 and \textsc{PRIMES Labex} ANR-11-LABX-0063/ ANR-11-IDEX-0007 research grants.}

### 2015-10-23 latex/article.tex
article

\begin{figure}
  \vspace{-0.35cm}
  \begin{center}
    {\includegraphics[width=4cm]{figs/approx1}}
    {\includegraphics[width=4cm]{figs/approx-reg-1}}
    {\includegraphics[width=4cm]{figs/approx-reg-2}}
  \end{center}
  \vspace{-0.35cm}
  \caption{Integral computation with an area estimation (\emph{left}) from pixel
    counting (\emph{middle}) or from densities (represented by different
    gray values) in a mipmap approximation of $\Shape$ (\emph{right}).}
  \label{fig:approx}
  \vspace{-0.35cm}
\end{figure}

@@

\begin{figure}
  \vspace{-0.35cm}
  \begin{center}
    {\includegraphics[width=4cm]{figs/approx-bh}}
    {\includegraphics[width=4cm]{figs/approx-ada}}
  \end{center}
  \vspace{-0.35cm}
  \caption{Adaptive approximation of the integration using a
    hierarchical decomposition of the ball $\Ball{R}{\vx}$ (\emph{left}), or a decomposition of $\Ball{R}{\vx}\cap\Shape$ (\emph{right}).}
  \label{fig:approx2}
\end{figure}

@@

\begin{figure}
  \vspace{-0.35cm}
  \begin{center}
    {\includegraphics[width=2.2cm]{figs/Octa_mean}}
    {\includegraphics[width=2.2cm]{figs/Octa_gaussian}}
%    {\includegraphics[width=2.7cm]{figs/Octa_k1}}
%    {\includegraphics[width=2.7cm]{figs/Octa_k2}}\\
%    {\includegraphics[width=2.7cm]{figs/Octa_dir_min}}
%    {\includegraphics[width=2.7cm]{figs/Octa_dir_max}}
    {\includegraphics[height=2.0cm]{figs/Octa_dir_min_zoom}}
    {\includegraphics[height=2.0cm]{figs/Octa_dir_max_zoom}}\\
    % {\includegraphics[height=4.0cm]{figs/EG_dragon_normal_zoom}}
    {\includegraphics[width=2.2cm]{figs/function_mean_0}}
    {\includegraphics[width=2.2cm]{figs/function_mean_1}}
    {\includegraphics[width=2.2cm]{figs/function_mean_2}}
    {\includegraphics[width=2.2cm]{figs/function_mean_3}}
    {\includegraphics[width=2.2cm]{figs/function_mean_4}}
  \end{center}

  \vspace{-0.35cm}
  \caption{\emph{First row}: Mean and Gaussian curvature estimation, (zoom of) first and second principal directions estimation on an OctaFlower with a digital domain of $130^3$.
  % \emph{Second row:} (Zoom of) First and second principal directions estimation on an OctaFlower.
  \emph{Second row:} Mean curvature computed in real-time on a dynamic object.}
  \label{fig:full}
\end{figure}

@@

We can thus get an approximated visualisation of our object as soon as we run
the application, allowing for real time interactions with the object (changing
the visualized value, curvature radius, \ldots). It is also clear on those
graphs that using a hierarchical decomposition reduces the curvature computation
time, especially with big radii. For the XYZ-Dragon with $R=20$, it needs almost
4 seconds to compute the $l_0$ level, whereas using the hierarchical algorithm,
it only needs 700ms. However, due to the precomputation and current hierarchical
structure, this algorithm is biased and creates an error (presented in
Table~\ref{tab:full-res-stat}) that needs to be considered.

\begin{figure}
  \vspace{-0.35cm}
  \begin{center}
    {\includegraphics[height=3.5cm]{figs/xyzrgb_dragon-510_R8_mean}}
    {\includegraphics[height=3.0cm]{figs/snow_I08iso_233_r20_l0_m3}}
  \end{center}
  \caption{Illustration of mean curvature computation of two large datasets: XYZ-Dragon (with digital domain of $512^3$) and Snow microstructures ($233^3$).}
  \label{fig:adaptive}
  \vspace{-0.35cm}
\end{figure}

Figure~\ref{fig:adaptive} shows curvature computation and exploration in
real-time on large datasets: XYZ-Dragon (with digital domain of $512^3$) and
Snow microstructures ($233^3$).

@@

This framework could also be used for feature detection purposes
such as presented in \cite{SMI2015}. The point classification is done by computing
the curvature at different radii and comparing them. Using our framework,
this may be done in a real-time manner.
The computed curvature could finally be used to control the refinement of the
triangulation. We are for now only using the normal computation for shading
purposes but we could imagine using it along with the vertices to do a
Poisson reconstruction of the object.

>>>>

\begin{figure}
  \vspace{-0.35cm}
  \begin{center}
    {\includegraphics[width=4.0cm]{figs/approx1}}
    {\includegraphics[width=4.0cm]{figs/approx-reg-1}}
    {\includegraphics[width=4.0cm]{figs/approx-reg-2}}
  \end{center}
  \vspace{-0.35cm}
  \caption{Integral computation with an area estimation (\emph{left}) from pixel
    counting (\emph{middle}) or from densities (represented by different
    gray values) in a mipmap approximation of $\Shape$ (\emph{right}).}
  \label{fig:approx}
  \vspace{-0.35cm}
\end{figure}

@@

\begin{figure}
  \vspace{-0.35cm}
  \begin{center}
    {\includegraphics[width=4cm]{figs/approx-bh}}
    {\includegraphics[width=4cm]{figs/approx-ada}}
  \end{center}
  \vspace{-0.35cm}
  \caption{Adaptive approximation of the integration using a
    hierarchical decomposition of the ball $\Ball{R}{\vx}$ (\emph{left}), or a decomposition of $\Ball{R}{\vx}\cap\Shape$ (\emph{right}).}
  \label{fig:approx2}
  \vspace{-0.35cm}
\end{figure}

@@

\begin{figure}
  \vspace{-0.35cm}
  \begin{center}
    {\includegraphics[width=2.2cm]{figs/Octa_mean}}
    {\includegraphics[width=2.2cm]{figs/Octa_gaussian}}
%    {\includegraphics[width=2.7cm]{figs/Octa_k1}}
%    {\includegraphics[width=2.7cm]{figs/Octa_k2}}\\
%    {\includegraphics[width=2.7cm]{figs/Octa_dir_min}}
%    {\includegraphics[width=2.7cm]{figs/Octa_dir_max}}
    {\includegraphics[height=2.0cm]{figs/Octa_dir_min_zoom}}
    {\includegraphics[height=2.0cm]{figs/Octa_dir_max_zoom}}\\
    % {\includegraphics[height=4.0cm]{figs/EG_dragon_normal_zoom}}
    {\includegraphics[width=2.2cm]{figs/function_mean_0}}
    {\includegraphics[width=2.2cm]{figs/function_mean_1}}
    {\includegraphics[width=2.2cm]{figs/function_mean_2}}
    {\includegraphics[width=2.2cm]{figs/function_mean_3}}
    {\includegraphics[width=2.2cm]{figs/function_mean_4}}
  \end{center}
  \vspace{-0.35cm}
  \caption{\emph{First row}: Mean and Gaussian curvature estimation, (zoom of) first and second principal directions estimation on an OctaFlower with a digital domain of $130^3$.
  % \emph{Second row:} (Zoom of) First and second principal directions estimation on an OctaFlower.
  \emph{Second row:} Mean curvature computed in real-time on a dynamic object.}
  \label{fig:full}
  \vspace{-0.35cm}
\end{figure}

@@

We can thus get an approximated visualisation of our object as soon as we run
the application, allowing for real time interactions with the object (changing
the visualized value, curvature radius, \ldots). It is also clear on those
graphs that using a hierarchical decomposition reduces the curvature computation
time, especially with big radii. For the XYZ-Dragon with $R=20$, it needs almost
4 seconds to compute the $l_0$ level, whereas using the hierarchical algorithm,
it only needs 700ms. However, due to the precomputation and current hierarchical
structure, this algorithm is biased and creates an error (presented in
Table~\ref{tab:full-res-stat}) that needs to be considered.
%
% \begin{figure}
%   \vspace{-0.35cm}
%   \begin{center}
%     {\includegraphics[height=3.5cm]{figs/xyzrgb_dragon-510_R8_mean}}
%     {\includegraphics[height=3.0cm]{figs/snow_I08iso_233_r20_l0_m3}}
%   \end{center}
%   \caption{Illustration of mean curvature computation of two large datasets: XYZ-Dragon (with digital domain of $512^3$) and Snow microstructures ($233^3$).}
%   \label{fig:adaptive}
%   \vspace{-0.35cm}
% \end{figure}
%
% Figure~\ref{fig:adaptive} shows curvature computation and exploration in
% real-time on large datasets: XYZ-Dragon (with digital domain of $512^3$) and
% Snow microstructures ($233^3$).

@@

% This framework could also be used for feature detection purposes such as
% presented in \cite{SMI2015}. The point classification is done by computing the
% curvature at different radii and comparing them. Using our framework, this may
% be done in a real-time manner. The computed curvature could finally be used to
% control the refinement of the triangulation. We are for now only using the
% normal computation for shading purposes but we could imagine using it along with
% the vertices to do a Poisson reconstruction of the object.
